Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-12 journal paper/content/related_work.tex
Minor edits.

Exploration-separating algorithms completely separate exploration and exploitation. The simplest approach, called \emph{Explore-First}, is to explore uniformly for a predetermined number of rounds, then choose one arm and ``exploit". A slightly more refined approach, called \emph{Epsilon-Greedy}, explores uniformly in each round $t$ with predetermined probability $\eps_t$, and exploits with the remaining probability.

@@

%A formal definition is that the distribution over arms in each round does not depend on rewards observed in the previous rounds.

>>>>

Exploration-separating algorithms completely separate exploration and exploitation. The simplest approach, called \emph{Explore-First}, is to explore uniformly for a predetermined number of rounds, then choose one arm and ``exploit". A slightly more refined approach, called \emph{Epsilon-Greedy}, explores uniformly in each round $t$ with predetermined probability $\eps_t$, and exploits with the remaining probability. A formal definition is that each round is either selected exploration, in which case  the distribution over arms does not depend on data, or it is assigned to exploitation, in which case the data from this round is discarded. The $T^{2/3}$ lower bound on regret follows from a somewhat more general lower bound in \citet{MechMAB-ec09}.

@@
